Doppler Imaging Fun

### 2019-07-03 tex/gitlinks.tex
stuff

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/91e40d1f56ca84e6a02a7a8d0a650deefdd735aa/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5f045717b27f4123fcdb1f0bcc4048d6ec47be9/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-03 tex/ms.tex
stuff

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/g_rigid.pdf}
    \oscaption{g_rigid}{%
        The Doppler $\mathbf{g}$ basis for a rigidly rotating star
        computed from Equation~(\ref{eq:rigid:gT}) and
        Equation~(\ref{eq:rigid:sTAnalytic}) up to spherical 
        harmonic degree $l=10$. Rows correspond to the degree $l$ and
        columns correspond to the order $m$. These functions encode
        the contribution of each spherical harmonic to the rotational
        broadening of features in the stellar spectrum. Because the
        rotational axis is chosen to be aligned with $\hat{y}$,
        none of the $m < 0$ harmonics contribute
        \label{fig:g_rigid}
    }
    \end{centering}
\end{figure}

@@

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.6\linewidth]{figures/spot_rigid.pdf}
    \oscaption{spot_rigid}{%
        A caption.
        \label{fig:spot_rigid}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.65\linewidth]{figures/compare_rigid.pdf}
    \oscaption{compare_rigid}{%
        A caption.
        \label{fig:compare_rigid}
    }
    \end{centering}
\end{figure}

>>>>

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/g_rigid.pdf}
    \oscaption{g_rigid}{%
        The Doppler $\mathbf{g}$ basis for a rigidly rotating star
        computed from Equation~(\ref{eq:rigid:gT}) and
        Equation~(\ref{eq:rigid:sTAnalytic}) up to spherical 
        harmonic degree $l=10$. Rows correspond to the degree $l$ and
        columns correspond to the order $m$. These functions encode
        the contribution of each spherical harmonic to the rotational
        broadening of features in the stellar spectrum. Because the
        rotational axis is chosen to be aligned with $\hat{y}$,
        none of the $m < 0$ harmonics contribute to the observed
        spectrum.
        \label{fig:g_rigid}
    }
    \end{centering}
\end{figure}

@@

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.6\linewidth]{figures/spot_rigid.pdf}
    \oscaption{spot_rigid}{%
        Time evolution of a Gaussian absorption line on a rigidly rotating, 
        spotted star computed from the analytic formulae in \S\ref{sec:rigid}.
        The stellar surface is modeled as a spherical harmonic expansion
        up to $l=20$, and the line shape is assumed to be the same everywhere;
        the spot simply downweights the local intensity at all wavelengths.
        As the spot rotates into view (left panel), the line shape changes
        slightly (center panel). The residuals between the line when the
        spot is in view (solid) and when it is on the backside of the star
        (dotted) are shown in the right panel, where
        a Gaussian-like feature can be seen tracking the spot as it rotates
        from the blueshifted hemisphere to the redshifted hemisphere of
        the star.
        \label{fig:spot_rigid}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.65\linewidth]{figures/compare_rigid.pdf}
    \oscaption{compare_rigid}{%
        The observed spectrum when the spot is in view computed with
        \starry (blue) and numerically (orange). The problem setup
        is the same as that in Figure~\ref{fig:spot_rigid}. The bottom
        panel shows the absolute value of the difference between the 
        two spectra for different grid resolutions in the numerical solution.
        As the number of grid points increases, the numerical solution
        converges to the \starry solution.
        \label{fig:compare_rigid}
    }
    \end{centering}
\end{figure}
